Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-17 Supplemental-Material-B-Annotated-Analysis.Rmd
clean up

```{r setup, include=FALSE}
# R Studio Clean-Up
  cat("\014") # clear console
  #rm(list=ls()) # clear workspace - use restart R instead [cmd/alt + shift + F10]
  gc() # garbage collector

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file 
lib <- c("rmarkdown", "knitr", "remedy", "bookdown", "psych",
         "ggplot2", "ggthemes", "haven", "RColorBrewer", "plotly", "gridExtra", "ggpattern",
         "lme4", "nlme", "jtools", "gtsummary",
         "sessioninfo", "tibble", "pander", "devtools", "mada",
         "data.table", "plyr", "dplyr", "tidyr", "Hmisc", "kableExtra", "papaja",
         "stringr", "stringi", "reshape2", "lubridate")
invisible(lapply(lib, library, character.only = TRUE))  
rm(lib)

@@

# Markdown Options
  knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # set working directory
  knitr::opts_knit$get("root.dir") # check working directory
  options(scipen = 999, digits = 4, width = 400) #removes scientific quotation
  #knitr::opts_chunk$set(echo = TRUE, cache = F, cache.path = rprojroot::find_rstudio_root_file('cache/')) # cache settings
  knitr::knit_hooks$set(
   error = function(x, options) {
     paste('\n\n<div class="alert alert-danger">',
           gsub('##', '\n', gsub('^##\ Error', '**Error**', x)),
           '</div>', sep = '\n')
   },
   warning = function(x, options) {
     paste('\n\n<div class="alert alert-warning">',
           gsub('##', '\n', gsub('^##\ Warning:', '**Warning**', x)),
           '</div>', sep = '\n')
   },
   message = function(x, options) {
     paste('\n\n<div class="alert alert-info">',
           gsub('##', '\n', x),
           '</div>', sep = '\n')
   }
  )
  htmltools::tagList(rmarkdown::html_dependency_font_awesome())

# Global Chunk Options
  knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figures/',
                        echo=TRUE, warning=FALSE, message=FALSE)
```

@@

# young medical professionals
dtMedical <- list(
  raw.pre = c(),
  raw.post = c(),
  raw.daily = c()
)

```

@@

# create data frame with cleaned data
  df <- dtWorker$combined %>%
    filter(Finished.pre == 1,
           Finished.daily == 1,
           !is.na(ExternalReference))

# add running number as measurement ID within participants   
  df$measureID = rowidv(df, cols = c("ExternalReference"))

  df <- df %>%
    mutate(
      PID = as.numeric(factor(ExternalReference)), # participant ID
      TID = measureID-1, # time ID with t0 = 0 for meaningfull intercept interpretations
      date = substr(StartDate,1,10), # awkward way of extracting date (best converted to )
      time = substr(StartDate,12,19), # awkward way of extracting time
      daynum = as.numeric(factor(date)), # all days as numeric for ordering
      daycor = ifelse(daytime=="morning" & period_to_seconds(hms(time))<period_to_seconds(hms("12:00:00")) | daytime=="afternoon" & period_to_seconds(hms(time))<period_to_seconds(hms("19:00:00")),daynum-1,daynum), # correctly identify which date the questionnaire is about
      daycor.lead = sprintf("%02d", daycor),
      daytime.lt = ifelse(daytime=="morning","a","b"), # morning / afternoon to a / b 
      day_time = paste(daycor.lead, daytime.lt, sep="_"), # combine day id with morning / afternoon
      session = as.numeric(factor(day_time)), # day and time identifier as numeric id
      SubTime = chron::times(time.0),
      time.daily = as.character(time.daily),
      PPDate = as.Date(df$date.daily),
      number = replace_na(number, 0),
      NonDutchNum = replace_na(NonDutchNum, 0)
    )

@@

# Export reduced Data
  #write.csv(dtWorker$clean, "data/processed/MT_clean-merged_07-05-2018.csv", row.names = F)
  #save(dtWorker$clean, file = "data/processed/MT_clean-merged_07-05-2018.RData")
```

@@

# Prepare dfs for Cleaning
df.pre <- dtStudents$raw.pre %>%
  mutate_all(na_if,"") %>%
  mutate_all(na_if,"NA") %>%
  filter(!is.na(ended)) %>% # remove all who did not finish
  filter(!e_mail %in% .$e_mail[duplicated(.$e_mail)]) %>% # remove all who did the pre questionnaire multiple times (b/c inconsistent ratings scales)
  filter(!session %in% ownIDs) %>% # remove our own test 
  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)

df.post <- dtStudents$raw.post %>%
  mutate_all(na_if,"") %>%
  mutate_all(na_if,"NA") %>%
  filter(!is.na(session)) %>% # remove own test runs
  filter(!session %in% ownIDs) %>% # remove our own test 
  filter(session %in% df.pre$session) %>% # remove anyone who wasn't in the pre
  filter(!is.na(ended)) %>% # remove all who never finished
  filter(!session %in% .$session[duplicated(.$session)]) %>% # remove all duplicate sessions
  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)

df.daily <- dtStudents$raw.daily %>%
  mutate_all(na_if,"") %>%
  mutate_all(na_if,"NA") %>%
  filter(!session %in% ownIDs) %>% # remove our own test 
  filter(session %in% df.pre$session) %>% # remove anyone who wasn't in the pre
  filter(!is.na(ended)) %>% # remove all who never finished
  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)

# merge daily with pre
dfPreDaily = merge(
  x = df.daily,
  y = df.pre,
  by = "session",
  suffixes = c(".daily", ".pre"),
  all = F
)

# merge daily with post 
dfCombined = merge(
  x = dfPreDaily,
  y = df.post,
  by = "session",
  suffixes = c(".pre", ".post"),
  all = F
)

@@

```{r cleanMedical}
#TBD
```

@@

# Time and Date Variables
  # remove seconds from afternoon time
  df$SubTime[df$daytime == "afternoon"] = paste0(substring(as.character(df$time.0[df$daytime == "afternoon"]),4,8),":00") 
  df$time.daily[df$daytime == "afternoon" & !is.na(df$time.daily!="<NA>")] = paste0(substring(as.character(df$time.daily[df$daytime == "afternoon" & !is.na(df$time.daily!="<NA>")]),4,8),":00")

  # Correct morning / afternoon date where survey was collected the day after to indicate the correct date that was targeted
  df$PPDate[df$SubTime < "11:50:00" & df$daytime == "morning"] = df$PPDate[df$SubTime < "11:50:00" & df$daytime == "morning"]-1
  df$PPDate[df$SubTime < "18:50:00" & df$daytime == "afternoon"] = df$PPDate[df$SubTime < "18:50:00" & df$daytime == "afternoon"]-1

# Mood scales
  df$calmness.daily = rowSums(df[, c("calmness1", "calmness2")], na.rm = T)
  df$alertness.daily = rowSums(df[, c("alertness1", "alertness2")], na.rm =T)
  df$valence.daily = rowSums(df[, c("valence1", "valence2")], na.rm = T)

# Need scales
  df$keyMotiveFulfilled = rowSums(df[,c("keymotive_fulfillemt_1","keyMotive_noInt_fulf_1")], na.rm=T)
  df$autonomy.daily.all = rowSums(df[,c("autonomy_1","autonomy_NoInt_1")], na.rm=T)
  df$competence.daily.all = rowSums(df[,c("competence_1","competence_NoInt_1")], na.rm=T)
  #cor(df$relatedness_other_1, df$relatedness_self_1,use="complete.obs")
  df$relatedness.daily.all = rowMeans(df[,c("relatedness_other_1","relatedness_self_1","relatedness_1_NoInt_1")], na.rm=T)
  df$relatedness.daily.int = rowMeans(df[,c("relatedness_other_1","relatedness_self_1")], na.rm=T)

# summarize by participant (check that everything is within pp might not be the case for )
  between <- df %>%
    group_by(ExternalReference) %>%
    mutate(
      CtContactNL = sum(Contact_dum),
      CtContactNonNl = sum(inNonDutch),
      CtContactNLAll = sum(number),
      CtContactNonNlAll = sum(NonDutchNum),
      AvKeyNeed = mean(keyMotiveFulfilled, na.rm=T),
      AvKeyNeedInt = mean(keymotive_fulfillemt_1, na.rm=T),
      AvKeyNeedNoInt = mean(keyMotive_noInt_fulf_1, na.rm=T),
      AvAutonomy = mean(autonomy.daily.all, na.rm=T),
      AvCompetence = mean(competence.daily.all, na.rm=T),
      AvRelatedness = mean(relatedness.daily.all, na.rm=T),
      AvThermo = mean(thermometerDutch_1, na.rm=T),
      AvWB = mean(ExWB_1, na.rm=T)) %>%
    ungroup() %>%
    mutate(
      CtContactNL_c = scale(CtContactNL, scale = FALSE),
      AvKeyNeedInt_c = scale(AvKeyNeedInt, scale = FALSE),
      AvKeyNeed_c = scale(AvKeyNeed, scale = FALSE),
      CtContactNL_z = scale(CtContactNL, scale = TRUE),
      AvKeyNeedInt_z = scale(AvKeyNeedInt, scale = TRUE),
      AvKeyNeed_z = scale(AvKeyNeed, scale = TRUE)
    )

  warning("some variable transformations (esp. _c and _z) might be across all participants (i.e., not within PP).")

  dtWorker$full <- between

  rm(df, between)

  #save(df.btw, file = "data/processed/df.btw.RData")  
  #write_sav(df.btw, "data/processed/MT_clean-merged_pre-post.sav")

# export data to Mplus
  # df.mplus = remove_all_labels(select(df, PID, session, thermometerDutch_1, inNonDutch, Contact_dum, keyMotiveFulfilled, autonomy.daily.all, competence.daily.all, relatedness.daily.all))
  # names(df.mplus)= c("PID", "session", "att", "intin", "intout", "keymot", "aut", "comp", "rel")
  # mplus = df.mplus[order(df.mplus$PID, df.mplus$session),]
  # mplus.intcont = mplus[mplus$intout==1,]
  # prepareMplusData(mplus.intcont, "data/processed/dynamic-subset-intonly.dat")

```

@@

# Add ID variables
  df$PID = as.numeric(factor(df$session)) # participant ID

# order time
  df$TID <- factor(df$date_period, levels = unique(dtStudents$raw.daily$date_period))
  df$TIDnum <- as.numeric(df$TID) #get numeric TID

  # check whether time ordering worked
  df <- df %>%
    arrange(PID, TID) #%>%
    #View()

# Interaction as Factor
  df$interaction.f <- factor(df$Interaction, levels = c("no interaction", "Dutch", "Non-Dutch"))
  df$intNL <- ifelse(df$Interaction=="Dutch",1,0)
  df$intNonNL<- ifelse(df$Interaction=="Non-Dutch",1,0)

# ------------------------------------------------------------------------------------------------------------- 
#                                       Combine Variables
# -------------------------------------------------------------------------------------------------------------
# Relatedness
  pairs.panels.new(df[c("RelatednessSelf","RelatednessOther")], 
                              labels = c("I shared information about myself.", "X shared information about themselves."))
  df$RelatednessInteraction <- rowMeans(df[c("RelatednessSelf","RelatednessOther")], na.rm=T)
  df$RelatednessInteraction[df$RelatednessInteraction == "NaN"] <- NA
# Relatedness Overall (JANNIS NOT SURE THESE ARE CORRECT, CHANGE ROWS?; J: Changed "NaN" in df$RelatednessInteraction to NA() should work now)
  df$Relatedness <- rowMeans(df[,c("RelatednessInteraction", "RelatednessNoInteraction")], na.rm=T)
# Pro-Sociality
  df$ProSo <- rowMeans(df[,c("ProSo1", "ProSo2", "ProSo3", "ProSo4")], na.rm=T)
# Anti-Sociality
  df$AntiSo <- rowMeans(df[,c("AntiSo1", "AntiSo2", "AntiSo3", "AntiSo4")], na.rm=T)

# ------------------------------------------------------------------------------------------------------------- 
#                                 Add Variables related to interaction partner
# -------------------------------------------------------------------------------------------------------------
# create function for later lapply
createIntPartDf <- function(inp) {

  # prepare the dataframe so that we can forloop over it later
    tmp <- data.frame(CC = as.character(inp$CC),
                    NewCC = as.character(inp$NewCC),
                    NewName = as.character(inp$NewName),
                    NewCloseness = inp$NewCloseness,
                    NewGender = inp$NewGender,
                    NewEthnicity = as.character(inp$NewEthnicity),
                    NewRelationship = as.character(inp$NewRelationship))

    tmp$CC2 <- recode(tmp$CC, 'SOMEONE ELSE' = "NA")
    tmp$CC2 <- ifelse(tmp$CC == 1 | tmp$CC == "SOMEONE ELSE", as.character(tmp$NewName), as.character(tmp$CC2)) 
    # maybe add [[:space:]]\b to remove space before word boundary or ^[[:space:]] to remove space in the beginning of a string
    tmp$CC2 <- gsub("^[[:space:]]", "", tmp$CC2)
    tmp$NewName <- gsub("^[[:space:]]", "", tmp$NewName)

@@

    # Run the for-loop. It finds the variables related to the name of the interaction partner. If there is a repeating interaction
    # partner (i.e. CC2) it takes the value (i.e. NewCloseness) from the first interaction (i.e. NewName)
      for (i in 1:nrow(tmp)) {
         if (is.na(tmp$CC2[i])) {
           next
         } else {
           tmp$closeness[i] <- na.omit(tmp$NewCloseness[as.character(tmp$CC2[i]) == as.character(tmp$NewName)])[1] #find closeness where CC2 matches NewName (na.omit + [1] to get the number)
           tmp$gender[i] <- na.omit(tmp$NewGender[as.character(tmp$CC2[i]) == as.character(tmp$NewName)])[1] #(na.omit + [1] to get the number and not the rest of the na.omit list)
           tmp$ethnicity[i] <- na.omit(as.character(tmp$NewEthnicity[as.character(tmp$CC2[i]) == as.character(tmp$NewName)]))[1] #PROBLEM IS THAT THERE ARE TOO MANY NA's: Difficult to deal with
           tmp$relationship[i] <- na.omit(as.character(tmp$NewRelationship[as.character(tmp$CC2[i]) == as.character(tmp$NewName)]))[1]
         }
      }

@@

# split df per participants and run function
  PP <- split(df, df$PID)
  PP <- lapply(PP, createIntPartDf); rm(createIntPartDf)

# add variables back to df
  remergePP <- do.call(rbind.data.frame, PP)
    colnames(remergePP) <- paste(colnames(remergePP), "_Calc", sep = "")
df <- cbind(df, remergePP);rm(remergePP)

@@

# store
  dtStudents$full = df
```

@@

```{r WorkerFreqAttCor}
# prepare data
workerContactFreq <- dtWorker$full %>% 
  group_by(ExternalReference) %>%
  summarise(
    n = n(),
    SumContactNL = sum(Contact_dum),
    PercContactNL = SumContactNL/n*100,
    SumContactNLAll = sum(number),
    AvAttitude = mean(thermometerDutch_1, na.rm=T)
  ) %>%
  mutate(
    WinSumContactNL = DescTools::Winsorize(SumContactNL),
    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
  )

# correlation panel 
pairs.panels.new(workerContactFreq %>% select(SumContactNL, SumContactNLAll, AvAttitude), 
                 labels = c("Sum:\nNumer of beeps with Outgroup Contact (NL)", 
                            "Sum:\nNumber of Outgroup Contacts (NL)", 
                            "Mean:\nOutgroup Attitudes (NL)"))

# correlation panel with interaction sums winsorized
pairs.panels.new(workerContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvAttitude), 
                 labels = c("Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]", 
                            "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]", 
                            "Mean:\nOutgroup Attitudes (NL)"))
```

@@

```{r workerInteractionTypePlt, fig.height=12}
workerContactType <- dtWorker$full %>% 
  group_by(
    Contact_dum,
    inNonDutch
    ) %>%
  summarise(
    n = n(),
    AttitudeM = mean(thermometerDutch_1, na.rm=T),
    AttitudeSD = sd(thermometerDutch_1, na.rm=T),
    AttitudeSE = AttitudeSD/sqrt(n),
    AttitudeLwr = AttitudeM - 1.96*AttitudeSE,
    AttitudeUpr = AttitudeM + 1.96*AttitudeSE
  ) %>%
  ungroup %>%
  mutate(
    InteractionType = paste(
      ifelse(Contact_dum == 1, "Out", "NoOut"),
      ifelse(inNonDutch == 1, "In", "NoIn"),
      sep = ", "
    )
  )

>>>>

```{r setup, include=FALSE}
# R Studio Clean-Up
cat("\014") # clear console
# rm(list=ls()) # clear workspace - use restart R instead [cmd/alt + shift + F10]
gc() # garbage collector

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file
lib <- c(
  "rmarkdown",
  "knitr",
  "remedy",
  "bookdown",
  "brms",
  "psych",
  "ggplot2",
  "ggthemes",
  "haven",
  "RColorBrewer",
  "plotly",
  "gridExtra",
  "ggpattern",
  "lme4",
  "nlme",
  "jtools",
  "gtsummary",
  "sessioninfo",
  "tibble",
  "pander",
  "devtools",
  "mada",
  "data.table",
  "plyr",
  "dplyr",
  "tidyr",
  "Hmisc",
  "kableExtra",
  "papaja",
  "stringr",
  "stringi",
  "reshape2",
  "lubridate"
)
invisible(lapply(lib, library, character.only = TRUE))
rm(lib)

@@

# Markdown Options
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # set working directory
knitr::opts_knit$get("root.dir") # check working directory
options(
  scipen = 999,
  digits = 4,
  width = 400
) # removes scientific quotation
# knitr::opts_chunk$set(echo = TRUE, cache = F, cache.path = rprojroot::find_rstudio_root_file('cache/')) # cache settings
knitr::knit_hooks$set(
  error = function(x, options) {
    paste('\n\n<div class="alert alert-danger">',
      gsub("##", "\n", gsub("^##\ Error", "**Error**", x)),
      "</div>",
      sep = "\n"
    )
  },
  warning = function(x, options) {
    paste('\n\n<div class="alert alert-warning">',
      gsub("##", "\n", gsub("^##\ Warning:", "**Warning**", x)),
      "</div>",
      sep = "\n"
    )
  },
  message = function(x, options) {
    paste('\n\n<div class="alert alert-info">',
      gsub("##", "\n", x),
      "</div>",
      sep = "\n"
    )
  }
)
htmltools::tagList(rmarkdown::html_dependency_font_awesome())

# Global Chunk Options
knitr::opts_chunk$set(
  fig.width = 12,
  fig.height = 8,
  fig.path = "Figures/",
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)
```

@@

# young medical professionals
dtMedical <- list(
  raw.pre = c(),
  raw.post = c(),
  raw.daily = c()
)
```

@@

# create data frame with cleaned data
df <- dtWorker$combined %>%
  filter(
    Finished.pre == 1,
    Finished.daily == 1,
    !is.na(ExternalReference)
  )

# add running number as measurement ID within participants
df$measureID <- rowidv(df, cols = c("ExternalReference"))

df <- df %>%
  mutate(
    PID = as.numeric(factor(ExternalReference)),
    # participant ID
    TID = measureID - 1,
    # time ID with t0 = 0 for meaningfull intercept interpretations
    date = substr(StartDate, 1, 10),
    # awkward way of extracting date (best converted to )
    time = substr(StartDate, 12, 19),
    # awkward way of extracting time
    daynum = as.numeric(factor(date)),
    # all days as numeric for ordering
    daycor = ifelse(
      daytime == "morning" &
        period_to_seconds(hms(time)) < period_to_seconds(hms("12:00:00")) |
        daytime == "afternoon" &
          period_to_seconds(hms(time)) < period_to_seconds(hms("19:00:00")),
      daynum - 1,
      daynum
    ),
    # correctly identify which date the questionnaire is about
    daycor.lead = sprintf("%02d", daycor),
    daytime.lt = ifelse(daytime == "morning", "a", "b"),
    # morning / afternoon to a / b
    day_time = paste(daycor.lead, daytime.lt, sep = "_"),
    # combine day id with morning / afternoon
    session = as.numeric(factor(day_time)),
    # day and time identifier as numeric id
    SubTime = chron::times(time.0),
    time.daily = as.character(time.daily),
    PPDate = as.Date(df$date.daily),
    number = replace_na(number, 0),
    NonDutchNum = replace_na(NonDutchNum, 0)
  )

@@

# Export reduced Data
# write.csv(dtWorker$clean, "data/processed/MT_clean-merged_07-05-2018.csv", row.names = F)
# save(dtWorker$clean, file = "data/processed/MT_clean-merged_07-05-2018.RData")
```

@@

# Prepare dfs for Cleaning
df.pre <- dtStudents$raw.pre %>%
  mutate_all(na_if, "") %>%
  mutate_all(na_if, "NA") %>%
  filter(!is.na(ended)) %>% # remove all who did not finish
  filter(!e_mail %in% .$e_mail[duplicated(.$e_mail)]) %>% # remove all who did the pre questionnaire multiple times (b/c inconsistent ratings scales)
  filter(!session %in% ownIDs) %>% # remove our own test
  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)

df.post <- dtStudents$raw.post %>%
  mutate_all(na_if, "") %>%
  mutate_all(na_if, "NA") %>%
  filter(!is.na(session)) %>% # remove own test runs
  filter(!session %in% ownIDs) %>% # remove our own test
  filter(session %in% df.pre$session) %>% # remove anyone who wasn't in the pre
  filter(!is.na(ended)) %>% # remove all who never finished
  filter(!session %in% .$session[duplicated(.$session)]) %>% # remove all duplicate sessions
  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)

df.daily <- dtStudents$raw.daily %>%
  mutate_all(na_if, "") %>%
  mutate_all(na_if, "NA") %>%
  filter(!session %in% ownIDs) %>% # remove our own test
  filter(session %in% df.pre$session) %>% # remove anyone who wasn't in the pre
  filter(!is.na(ended)) %>% # remove all who never finished
  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)

# merge daily with pre
dfPreDaily <- merge(
  x = df.daily,
  y = df.pre,
  by = "session",
  suffixes = c(".daily", ".pre"),
  all = F
)

# merge daily with post
dfCombined <- merge(
  x = dfPreDaily,
  y = df.post,
  by = "session",
  suffixes = c(".pre", ".post"),
  all = F
)

@@

```{r cleanMedical}
# TBD
```

@@

# Time and Date Variables
# remove seconds from afternoon time
df$SubTime[df$daytime == "afternoon"] <- paste0(substring(as.character(df$time.0[df$daytime == "afternoon"]), 4, 8), ":00")
df$time.daily[df$daytime == "afternoon" &
  !is.na(df$time.daily != "<NA>")] <- paste0(substring(as.character(df$time.daily[df$daytime == "afternoon" &
  !is.na(df$time.daily != "<NA>")]), 4, 8), ":00")

# Correct morning / afternoon date where survey was collected the day after to indicate the correct date that was targeted
df$PPDate[df$SubTime < "11:50:00" &
  df$daytime == "morning"] <- df$PPDate[df$SubTime < "11:50:00" &
  df$daytime == "morning"] - 1
df$PPDate[df$SubTime < "18:50:00" &
  df$daytime == "afternoon"] <- df$PPDate[df$SubTime < "18:50:00" &
  df$daytime == "afternoon"] - 1

# Mood scales
df$calmness.daily <- rowSums(df[, c("calmness1", "calmness2")], na.rm = T)
df$alertness.daily <- rowSums(df[, c("alertness1", "alertness2")], na.rm = T)
df$valence.daily <- rowSums(df[, c("valence1", "valence2")], na.rm = T)

# Need scales
df$keyMotiveFulfilled <- rowSums(df[, c("keymotive_fulfillemt_1", "keyMotive_noInt_fulf_1")], na.rm = T)
df$autonomy.daily.all <- rowSums(df[, c("autonomy_1", "autonomy_NoInt_1")], na.rm = T)
df$competence.daily.all <- rowSums(df[, c("competence_1", "competence_NoInt_1")], na.rm = T)
# cor(df$relatedness_other_1, df$relatedness_self_1,use="complete.obs")
df$relatedness.daily.all <- rowMeans(df[, c(
  "relatedness_other_1",
  "relatedness_self_1",
  "relatedness_1_NoInt_1"
)], na.rm = T)
df$relatedness.daily.int <- rowMeans(df[, c("relatedness_other_1", "relatedness_self_1")], na.rm = T)

# summarize by participant (check that everything is within pp might not be the case for )
between <- df %>%
  group_by(ExternalReference) %>%
  mutate(
    CtContactNL = sum(Contact_dum),
    CtContactNonNl = sum(inNonDutch),
    CtContactNLAll = sum(number),
    CtContactNonNlAll = sum(NonDutchNum),
    AvKeyNeed = mean(keyMotiveFulfilled, na.rm = T),
    AvKeyNeedInt = mean(keymotive_fulfillemt_1, na.rm = T),
    AvKeyNeedNoInt = mean(keyMotive_noInt_fulf_1, na.rm = T),
    AvAutonomy = mean(autonomy.daily.all, na.rm = T),
    AvCompetence = mean(competence.daily.all, na.rm = T),
    AvRelatedness = mean(relatedness.daily.all, na.rm = T),
    AvThermo = mean(thermometerDutch_1, na.rm = T),
    AvWB = mean(ExWB_1, na.rm = T)
  ) %>%
  ungroup() %>%
  mutate(
    CtContactNL_c = scale(CtContactNL, scale = FALSE),
    AvKeyNeedInt_c = scale(AvKeyNeedInt, scale = FALSE),
    AvKeyNeed_c = scale(AvKeyNeed, scale = FALSE),
    CtContactNL_z = scale(CtContactNL, scale = TRUE),
    AvKeyNeedInt_z = scale(AvKeyNeedInt, scale = TRUE),
    AvKeyNeed_z = scale(AvKeyNeed, scale = TRUE)
  )

warning(
  "some variable transformations (esp. _c and _z) might be across all participants (i.e., not within PP)."
)

dtWorker$full <- between
rm(df, between)

# Between participants contact frequency
workerContactFreq <- dtWorker$full %>%
  group_by(ExternalReference) %>%
  summarise(
    n = n(),
    SumContactNL = sum(Contact_dum),
    PercContactNL = SumContactNL / n * 100,
    SumContactNLAll = sum(number),
    AvAttitude = mean(thermometerDutch_1, na.rm = T)
  ) %>%
  mutate(
    WinSumContactNL = DescTools::Winsorize(SumContactNL),
    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
  )

# dataframe where interaction types are recoded
workerInteractionType <- dtWorker$full %>%
  mutate(
    OutgroupInteraction = as_factor(Contact_dum),
    NonOutgroupInteraction = as_factor(inNonDutch)
  )

# save cleaned data
# save(df.btw, file = "data/processed/df.btw.RData")
# write_sav(df.btw, "data/processed/MT_clean-merged_pre-post.sav")

# export data to Mplus
# df.mplus = remove_all_labels(select(df,
#                                     PID, session,
#                                     thermometerDutch_1, inNonDutch, Contact_dum,
#                                     keyMotiveFulfilled, autonomy.daily.all, competence.daily.all, relatedness.daily.all))
# names(df.mplus)= c("PID", "session", "att", "intin", "intout", "keymot", "aut", "comp", "rel")
# mplus = df.mplus[order(df.mplus$PID, df.mplus$session),]
# mplus.intcont = mplus[mplus$intout==1,]
# prepareMplusData(mplus.intcont, "data/processed/dynamic-subset-intonly.dat")
```

@@

# Add ID variables
df$PID <- as.numeric(factor(df$session)) # participant ID

# order time
df$TID <-
  factor(df$date_period, levels = unique(dtStudents$raw.daily$date_period))
df$TIDnum <- as.numeric(df$TID) # get numeric TID

# check whether time ordering worked
df <- df %>%
  arrange(PID, TID) # %>%
# View()

# Interaction as Factor
df$interaction.f <-
  factor(df$Interaction,
    levels = c("no interaction", "Dutch", "Non-Dutch")
  )
df$intNL <- ifelse(df$Interaction == "Dutch", 1, 0)
df$intNonNL <- ifelse(df$Interaction == "Non-Dutch", 1, 0)

# -------------------------------------------------------------------------------------------------------------
#                                       Combine Variables
# -------------------------------------------------------------------------------------------------------------
# Relatedness
pairs.panels.new(
  df[c("RelatednessSelf", "RelatednessOther")],
  labels = c(
    "I shared information about myself.",
    "X shared information about themselves."
  )
)
df$RelatednessInteraction <-
  rowMeans(df[c("RelatednessSelf", "RelatednessOther")], na.rm = T)
df$RelatednessInteraction[df$RelatednessInteraction == "NaN"] <-
  NA
# Relatedness Overall (JANNIS NOT SURE THESE ARE CORRECT, CHANGE ROWS?; J: Changed "NaN" in df$RelatednessInteraction to NA() should work now)
df$Relatedness <-
  rowMeans(df[, c("RelatednessInteraction", "RelatednessNoInteraction")],
    na.rm =
      T
  )
# Pro-Sociality
df$ProSo <-
  rowMeans(df[, c("ProSo1", "ProSo2", "ProSo3", "ProSo4")], na.rm = T)
# Anti-Sociality
df$AntiSo <-
  rowMeans(df[, c("AntiSo1", "AntiSo2", "AntiSo3", "AntiSo4")], na.rm = T)

# -------------------------------------------------------------------------------------------------------------
#                                 Add Variables related to interaction partner
# -------------------------------------------------------------------------------------------------------------
# create function for later lapply
createIntPartDf <- function(inp) {
  # prepare the dataframe so that we can forloop over it later
  tmp <- data.frame(
    CC = as.character(inp$CC),
    NewCC = as.character(inp$NewCC),
    NewName = as.character(inp$NewName),
    NewCloseness = inp$NewCloseness,
    NewGender = inp$NewGender,
    NewEthnicity = as.character(inp$NewEthnicity),
    NewRelationship = as.character(inp$NewRelationship)
  )

  tmp$CC2 <- recode(tmp$CC, "SOMEONE ELSE" = "NA")
  tmp$CC2 <-
    ifelse(
      tmp$CC == 1 |
        tmp$CC == "SOMEONE ELSE",
      as.character(tmp$NewName),
      as.character(tmp$CC2)
    )
  # maybe add [[:space:]]\b to remove space before word boundary or ^[[:space:]] to remove space in the beginning of a string
  tmp$CC2 <- gsub("^[[:space:]]", "", tmp$CC2)
  tmp$NewName <- gsub("^[[:space:]]", "", tmp$NewName)

@@

  # Run the for-loop. It finds the variables related to the name of the interaction partner. If there is a repeating interaction
  # partner (i.e. CC2) it takes the value (i.e. NewCloseness) from the first interaction (i.e. NewName)
  for (i in 1:nrow(tmp)) {
    if (is.na(tmp$CC2[i])) {
      next
    } else {
      tmp$closeness[i] <-
        na.omit(tmp$NewCloseness[as.character(tmp$CC2[i]) == as.character(tmp$NewName)])[1] # find closeness where CC2 matches NewName (na.omit + [1] to get the number)
      tmp$gender[i] <-
        na.omit(tmp$NewGender[as.character(tmp$CC2[i]) == as.character(tmp$NewName)])[1] # (na.omit + [1] to get the number and not the rest of the na.omit list)
      tmp$ethnicity[i] <-
        na.omit(as.character(tmp$NewEthnicity[as.character(tmp$CC2[i]) == as.character(tmp$NewName)]))[1] # PROBLEM IS THAT THERE ARE TOO MANY NA's: Difficult to deal with
      tmp$relationship[i] <-
        na.omit(as.character(tmp$NewRelationship[as.character(tmp$CC2[i]) == as.character(tmp$NewName)]))[1]
    }
  }

@@

# split df per participants and run function
PP <- split(df, df$PID)
PP <- lapply(PP, createIntPartDf)
rm(createIntPartDf)

# add variables back to df
remergePP <- do.call(rbind.data.frame, PP)
colnames(remergePP) <-
  paste(colnames(remergePP), "_Calc", sep = "")
df <- cbind(df, remergePP)
rm(remergePP, PP)

@@

# store
dtStudents$full <- df
rm(df)
```

@@

```{r WorkerFreqAttCor}
# correlation panel
pairs.panels.new(
  workerContactFreq %>% select(SumContactNL, SumContactNLAll, AvAttitude),
  labels = c(
    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
    "Sum:\nNumber of Outgroup Contacts (NL)",
    "Mean:\nOutgroup Attitudes (NL)"
  )
)

# correlation panel with interaction sums winsorized
pairs.panels.new(
  workerContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvAttitude),
  labels = c(
    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
    "Mean:\nOutgroup Attitudes (NL)"
  )
)
```

@@

```{r workerInteractionTypePlt, fig.height=12}
# between participants interaction type
workerContactType <- dtWorker$full %>%
  group_by(
    Contact_dum,
    inNonDutch
  ) %>%
  summarise(
    n = n(),
    AttitudeM = mean(thermometerDutch_1, na.rm = T),
    AttitudeSD = sd(thermometerDutch_1, na.rm = T),
    AttitudeSE = AttitudeSD / sqrt(n),
    AttitudeLwr = AttitudeM - 1.96 * AttitudeSE,
    AttitudeUpr = AttitudeM + 1.96 * AttitudeSE
  ) %>%
  ungroup() %>%
  mutate(InteractionType = paste(
    ifelse(Contact_dum == 1, "Out", "NoOut"),
    ifelse(inNonDutch == 1, "In", "NoIn"),
    sep = ", "
  ))
